Look-Ahead Screening Rules for the Lasso

### 2021-06-29 paper/main.tex
Update revision

Suppose, now, that we have solved the lasso for \(\lambda\); then
for any given \(\lambda^* \leq \lambda\);
the Gap Safe rule~\citep{ndiaye2017} discards the \(j\)th
predictor if
\begin{equation}
  \label{eq:gap-safe-rule}
  |X^T \theta_\lambda|_j + \lVert x_j\rVert_2
  \sqrt{\frac{1}{\lambda_*^2}
    G(\beta_\lambda, \theta_\lambda; \lambda^*)}
  < 1
\end{equation}
where
\[
  \theta_\lambda = \frac{y - X\beta_\lambda}{
    \max\big( |X^T(y - X\beta_\lambda)|, \lambda\big)}
\]
is a dual-feasible point~\cite{ndiaye2017} obtained through dual scaling.

@@

\begin{figure}[hbtp]
  \centering
  \includegraphics{figures/simulateddata-timings.pdf}
  \caption{Standard box plots of timings to fit a full lasso path to
    a simulated data set with \(n = 100\), \(p = 50\,000\), and five true
    signals.}
  \label{fig:simulated-data}
\end{figure}

@@

Moreover, the idea is general and can therefore be extended to any type of safe
screening rule and also used in tandem with heuristic screening rules in order
to avoid expensive KKT computations. Finally, although we only cover one type of
solver in our experiments, note that our screening method is
agnostic to the solver used to solve the lasso and that we therefore expect our
results to be generalizable.

>>>>

Suppose, now, that we have solved the lasso for \(\lambda\); then
for any given \(\lambda^* \leq \lambda\),
the Gap Safe rule~\citep{ndiaye2017} discards the \(j\)th
predictor if
\begin{equation} \label{eq:gap-safe-rule}
  |X^T \theta_\lambda|_j + \lVert x_j\rVert_2
  \sqrt{\frac{1}{\lambda_*^2}
    G(\beta_\lambda, \theta_\lambda; \lambda^*)}
  < 1
\end{equation}
where
\[
  \theta_\lambda = \frac{y - X\beta_\lambda}{
    \max\big( |X^T(y - X\beta_\lambda)|, \lambda\big)}
\]
is a dual-feasible point~\cite{ndiaye2017} obtained through dual scaling.

@@

\begin{figure}[hbtp]
  \centering
  \includegraphics{figures/simulated-data-timings.pdf}
  \caption{Standard box plots of timings to fit a full lasso path to
    a simulated data set with \(n = 100\), \(p = 50\,000\), and five true
    signals.}
  \label{fig:simulated-data}
\end{figure}

@@

Moreover, the idea is general and can therefore be extended to any type of safe
screening rule and also used in tandem with heuristic screening rules in order
to avoid expensive KKT computations. Finally, although we only cover one type
of cyclical
coordinate descent in our experiments, note that our screening method is
agnostic to the solver used and that we expect the results
hold for any solver that benefits from predictor screening.
